Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-10 Article.tex
Small paragraph added

\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
\label{fig:expNumDRX2}
\end{figure}

>>>>

\textcolor{purple}{To further demonstrate the validity of the proposed model as demonstrated during the identification for a strain rate $\mdot\varepsilon = 0.001\ps$, we carried out a comparison between the microstructure obtained experimentally for a strain $\varepsilon=0.55$ and its numerical correspondence for a reduction of $45\%$ as can be seen in Figure 16. This figure shows that recrystallization is not complete at the edge of the specimen, nor at the point of contact between the specimen and the anvils. This is why unrecrystallized grains can be seen. These observations are confirmed numerically. This further confirms the validity of the model.}
\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
\label{fig:expNumDRX2}
\end{figure}
